
\section*{Skippers' Meeting}

After a late night of deliberation, negotiation and inebriation, the Skipper As that are going on the holiday have decided amongst themselves who is legally in charge and which restaurant the group meal will take place in.

\subsection*{Boats - Initial Lists}

\subsubsection*{Codename ``Heracles''}
\textsf{Bavaria C45}

\subsubsection*{Codename ``Bellerophon''}
\textsf{Bavaria Cruiser 46}

\subsubsection*{Codename ``Odysseus''}
\textsf{Junneau Sun Odyssey 479}

\subsection*{Initial Idea for Route}
\begin{description}
\item[Cape Sounion] Anchorage in the bay below a famous temple to Poseidon.
\item[Poros] A Greek resort town with tavernas aplenty - and some fantastic anchoring en route
\item[Hydra] Some would argue the most beautiful Island in the Med. Great walks, boutique shops and a number of artistic houses (including Leonard Cohen) etc.  
\item[Dhokos] A caldera anchorage with space for a BBQ
\item[Perdika] A small fishing village perched on one of the most important sites of Greek mythology.  
\end{description}

\subsection*{Group Meal}

\href{https://www.hydra.com.gr/veranda-restaurant/en-index.html}{The Veranda Restaurant, Hydra.}

\subsection*{Suggested Reading}
\begin{itemize}
\item Heikell R, and Heikell L, ``West Aegean, 4th Edition'', Imray Laurie Norrie and Wilson, St. Ives, 2019\footnote{updates available}
\item Chart G14, ``Saronic and Argolic Gulfs'', Imray Laurie Norrie and Wilson, St. Ives, 2020\footnote{updates available}
\item Averbuck, A., Hall, R., et.al., ``Lonely Planet Greece (A Travel Guide), 16th Edition'', Lonely Planet, Fort Mill SC, USA, 2023
\end{itemize}